%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Jiachen He} % Your name
\address{5 2 \\ 19 Partick Bridge street, G11 6PN Glasgow, United Kingdom} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+44)07546284559 \\ 2252699h@student.gla.ac.uk} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Glasgow} \hfill {\em Septeber 2016 - Present} 
\\ Bachelor of science in Physics with Astrophysics, School of Physics \& Astronomy
\vspace{5pt}\\
{\bf Hongkong University of Science and Technology} \hfill {\em Septeber 2017 - June 2018}
\\ Bachelor of science(exchange) in Physics, School of Physics

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experiences}

\begin{rSubsection}{University \textit{of} Glasgow, University of Birmingham}{June 2019 - Present}{Gravitational Astronomy Group, Student}{Undergraduate Honour Project}
    \item Gravitational Wave detector laser path simulation.
    \item Narrow banding for detector sensitivity based on signal recycling cavity detuning.
    \item Testing of General Relativity, black-hole perturbation theory with black hole merger higher modes.
    \end{rSubsection}

\begin{rSubsection}{Universit\'{e} Paris Diderot, University of Glasgow}{September 2018 - March 2019}{LIGO-Virgo GWOSC Workshop, Student}{Gravitational Wave Project}
    \item Gravitational wave data analysis on data presentation, Fourier-based methods for noise deduction and whitening
    \& estimation on detection sensitivity of BNS range.
    \item Templates families evaluation for matched filtering on post-Newtonian, Numerical Relativity methods, filtering and whitening with 
    $\chi^2$ test.
    \item Parameter estimation with MCMC \& Bayesian analysis with Bibly.
    \end{rSubsection}

\begin{rSubsection}{National Astronomical Observatories, CAS}{June 2018 - August 2018}{Group of dark-matter and dark-energy, Research Assistant}{Cosmology Project}
    \item Individually finished parameter estimation on tidal effect on dwarf galaxies in galactic simulations.
    \item Noise deduction in 21CM H-line array with eigenvalue analysis on covariant matrix.
    \item Joint developing of DJI-drones as a artificial star \& measurement station with high accuracy with GPS differential technology for telescope array calibration.
    \end{rSubsection}

\begin{rSubsection}{Institute of Physics, Chinese Academy of Sciences(CAS)}{June 2017 - July 2017}{Superconductivity group 8, Research Assistant}{Internship on condensed matter}
\item Theoretical evaluation of iron-based superconductor with BCS theory.
\item Material manucaption for iron-based superconductor - crystal \& related circuit systems.
\end{rSubsection}
\end{rSection}
% \begin{rSection}{Desired Graduate school}
    
%     \begin{rSubsection}{Desired direction for graduate school}{}{}{}
%         \item Gravitational wave research(Numerical GR, Unmodeled waveform).
%         \item Numerical simulation.
%         \item Theoretical Cosmology \& Particle physics.
%     \end{rSubsection}
    
% \end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Courses \& Skills}

    \begin{rSubsection}{Physics \& Astronomy}{}{}{}
    \item General Physics \& Astrophysics. 
    \item Instruments on Gravitational wave, radio \& optical telescopes. Cosmology, General Relativity. Astronomical data analysis, Bayesian interferer. 
    \end{rSubsection} 
    
    \begin{rSubsection}{Programming}{}{}{}
    \item Python, Julia, Matlab, Mathematica, Git, Shell, Docker, PowerShell, \LaTeX.
    \item Machine learning \& Artificial Intelligence with Reinforcement Learning; 
    \item Server maintenance under Windows\&Linux.
    \end{rSubsection} 
    
    \end{rSection}

\end{document}